DataSetup

### 2022-02-17 DataSetup.Rmd
Added additional new names for smri variables

FS_LCort_GM_Vol
FS_RCort_GM_Vol
FS_TotCort_GM_Vol
FS_SubCort_GM_Vol
FS_Total_GM_Vol
FS_SupraTentorial_Vol
FS_SupraTentorial_Vol_No_Vent

@@

FS_R_Bankssts_Area
FS_R_Caudalanteriorcingulate_Area
FS_R_Caudalmiddlefrontal_Area
FS_R_Cuneus_Area
FS_R_Entorhinal_Area
FS_R_Fusiform_Area
FS_R_Inferiorparietal_Area
FS_R_Inferiortemporal_Area
FS_R_Isthmuscingulate_Area
FS_R_Lateraloccipital_Area
FS_R_Lateralorbitofrontal_Area
FS_R_Lingual_Area
FS_R_Medialorbitofrontal_Area
FS_R_Middletemporal_Area
FS_R_Parahippocampal_Area
FS_R_Paracentral_Area
FS_R_Parsopercularis_Area
FS_R_Parsorbitalis_Area
FS_R_Parstriangularis_Area
FS_R_Pericalcarine_Area
FS_R_Postcentral_Area
FS_R_Posteriorcingulate_Area
FS_R_Precentral_Area
FS_R_Precuneus_Area
FS_R_Rostralanteriorcingulate_Area
FS_R_Rostralmiddlefrontal_Area
FS_R_Superiorfrontal_Area
FS_R_Superiorparietal_Area
FS_R_Superiortemporal_Area
FS_R_Supramarginal_Area
FS_R_Frontalpole_Area
FS_R_Temporalpole_Area
FS_R_Transversetemporal_Area
FS_R_Insula_Area
FS_L_Bankssts_GrayVol
FS_L_Caudalanteriorcingulate_GrayVol
FS_L_Caudalmiddlefrontal_GrayVol
FS_L_Cuneus_GrayVol
FS_L_Entorhinal_GrayVol
FS_L_Fusiform_GrayVol
FS_L_Inferiorparietal_GrayVol
FS_L_Inferiortemporal_GrayVol
FS_L_Isthmuscingulate_GrayVol
FS_L_Lateraloccipital_GrayVol
FS_L_Lateralorbitofrontal_GrayVol
FS_L_Lingual_GrayVol
FS_L_Medialorbitofrontal_GrayVol
FS_L_Middletemporal_GrayVol
FS_L_Parahippocampal_GrayVol
FS_L_Paracentral_GrayVol
FS_L_Parsopercularis_GrayVol
FS_L_Parsorbitalis_GrayVol
FS_L_Parstriangularis_GrayVol
FS_L_Pericalcarine_GrayVol
FS_L_Postcentral_GrayVol
FS_L_Posteriorcingulate_GrayVol
FS_L_Precentral_GrayVol
FS_L_Precuneus_GrayVol
FS_L_Rostralanteriorcingulate_GrayVol
FS_L_Rostralmiddlefrontal_GrayVol
FS_L_Superiorfrontal_GrayVol
FS_L_Superiorparietal_GrayVol
FS_L_Superiortemporal_GrayVol
FS_L_Supramarginal_GrayVol
FS_L_Frontalpole_GrayVol
FS_L_Temporalpole_GrayVol
FS_L_Transversetemporal_GrayVol
FS_L_Insula_GrayVol
FS_R_Bankssts_GrayVol
FS_R_Caudalanteriorcingulate_GrayVol
FS_R_Caudalmiddlefrontal_GrayVol
FS_R_Cuneus_GrayVol
FS_R_Entorhinal_GrayVol
FS_R_Fusiform_GrayVol
FS_R_Inferiorparietal_GrayVol
FS_R_Inferiortemporal_GrayVol
FS_R_Isthmuscingulate_GrayVol
FS_R_Lateraloccipital_GrayVol
FS_R_Lateralorbitofrontal_GrayVol
FS_R_Lingual_GrayVol
FS_R_Medialorbitofrontal_GrayVol
FS_R_Middletemporal_GrayVol
FS_R_Parahippocampal_GrayVol
FS_R_Paracentral_GrayVol
FS_R_Parsopercularis_GrayVol
FS_R_Parsorbitalis_GrayVol
FS_R_Parstriangularis_GrayVol
FS_R_Pericalcarine_GrayVol
FS_R_Postcentral_GrayVol
FS_R_Posteriorcingulate_GrayVol
FS_R_Precentral_GrayVol
FS_R_Precuneus_GrayVol
FS_R_Rostralanteriorcingulate_GrayVol
FS_R_Rostralmiddlefrontal_GrayVol
FS_R_Superiorfrontal_GrayVol
FS_R_Superiorparietal_GrayVol
FS_R_Superiortemporal_GrayVol
FS_R_Supramarginal_GrayVol
FS_R_Frontalpole_GrayVol
FS_R_Temporalpole_GrayVol
FS_R_Transversetemporal_GrayVol
FS_R_Insula_GrayVol

>>>>

FS_LCort_GM_Vol = smri_vol_cdk_totallh
FS_RCort_GM_Vol = smri_vol_cdk_totalrh
FS_TotCort_GM_Vol = smri_vol_cdk_total #total whole brain cortical volume
FS_SubCort_GM_Vol = smri_vol_scs_subcorticalgv
FS_Total_GM_Vol #maybe just calculate?
FS_SupraTentorial_Vol = smri_vol_scs_suprateialv #assuming this includes all ventricles
FS_SupraTentorial_Vol_No_Vent  #smri_vol_scs_allventricles is all ventricles, subtract?

@@

FS_R_Bankssts_Area = smri_area_cdk_banksstsrh
FS_R_Caudalanteriorcingulate_Area = smri_area_cdk_cdacaterh
FS_R_Caudalmiddlefrontal_Area = smri_area_cdk_cdmdfrrh
FS_R_Cuneus_Area = smri_area_cdk_cuneusrh
FS_R_Entorhinal_Area = smri_area_cdk_ehinalrh
FS_R_Fusiform_Area = smri_area_cdk_fusiformrh
FS_R_Inferiorparietal_Area = smri_area_cdk_ifplrh
FS_R_Inferiortemporal_Area = 	smri_area_cdk_iftmrh
FS_R_Isthmuscingulate_Area = smri_area_cdk_ihcaterh
FS_R_Lateraloccipital_Area = smri_area_cdk_loccrh
FS_R_Lateralorbitofrontal_Area = smri_area_cdk_lobfrrh
FS_R_Lingual_Area = smri_area_cdk_lingualrh
FS_R_Medialorbitofrontal_Area = smri_area_cdk_mobfrrh
FS_R_Middletemporal_Area = smri_area_cdk_mdtmrh
FS_R_Parahippocampal_Area = smri_area_cdk_parahpalrh
FS_R_Paracentral_Area = smri_area_cdk_paracnrh
FS_R_Parsopercularis_Area = smri_area_cdk_parsopcrh
FS_R_Parsorbitalis_Area = smri_area_cdk_parsobisrh
FS_R_Parstriangularis_Area = smri_area_cdk_parstgrisrh
FS_R_Pericalcarine_Area = smri_area_cdk_periccrh
FS_R_Postcentral_Area = smri_area_cdk_postcnrh
FS_R_Posteriorcingulate_Area = smri_area_cdk_ptcaterh
FS_R_Precentral_Area = smri_area_cdk_precnrh
FS_R_Precuneus_Area = smri_area_cdk_pcrh
FS_R_Rostralanteriorcingulate_Area = smri_area_cdk_rracaterh
FS_R_Rostralmiddlefrontal_Area = smri_area_cdk_rrmdfrrh
FS_R_Superiorfrontal_Area = smri_area_cdk_sufrrh
FS_R_Superiorparietal_Area = 	smri_area_cdk_suplrh
FS_R_Superiortemporal_Area = smri_area_cdk_sutmrh
FS_R_Supramarginal_Area = smri_area_cdk_smrh
FS_R_Frontalpole_Area = smri_area_cdk_frpolerh
FS_R_Temporalpole_Area = smri_area_cdk_tmpolerh
FS_R_Transversetemporal_Area = smri_area_cdk_trvtmrh
FS_R_Insula_Area = 	smri_area_cdk_insularh
#abcd technically doesn't say gray matter volume for the following varibles
FS_L_Bankssts_GrayVol = smri_vol_cdk_banksstslh
FS_L_Caudalanteriorcingulate_GrayVol = smri_vol_cdk_cdacatelh
FS_L_Caudalmiddlefrontal_GrayVol = smri_vol_cdk_cdmdfrlh
FS_L_Cuneus_GrayVol = smri_vol_cdk_cuneuslh
FS_L_Entorhinal_GrayVol = smri_vol_cdk_ehinallh
FS_L_Fusiform_GrayVol = smri_vol_cdk_fusiformlh
FS_L_Inferiorparietal_GrayVol = smri_vol_cdk_ifpllh
FS_L_Inferiortemporal_GrayVol = smri_vol_cdk_iftmlh
FS_L_Isthmuscingulate_GrayVol = smri_vol_cdk_ihcatelh
FS_L_Lateraloccipital_GrayVol = smri_vol_cdk_locclh
FS_L_Lateralorbitofrontal_GrayVol = smri_vol_cdk_lobfrlh
FS_L_Lingual_GrayVol = smri_vol_cdk_linguallh
FS_L_Medialorbitofrontal_GrayVol = smri_vol_cdk_mobfrlh
FS_L_Middletemporal_GrayVol = smri_vol_cdk_mdtmlh
FS_L_Parahippocampal_GrayVol = smri_vol_cdk_parahpallh
FS_L_Paracentral_GrayVol = smri_vol_cdk_paracnlh
FS_L_Parsopercularis_GrayVol = smri_vol_cdk_parsopclh
FS_L_Parsorbitalis_GrayVol = smri_vol_cdk_parsobislh
FS_L_Parstriangularis_GrayVol = smri_vol_cdk_parstgrislh
FS_L_Pericalcarine_GrayVol = smri_vol_cdk_pericclh
FS_L_Postcentral_GrayVol = smri_vol_cdk_postcnlh
FS_L_Posteriorcingulate_GrayVol = smri_vol_cdk_ptcatelh
FS_L_Precentral_GrayVol = smri_vol_cdk_precnlh
FS_L_Precuneus_GrayVol = smri_vol_cdk_pclh
FS_L_Rostralanteriorcingulate_GrayVol = smri_vol_cdk_rracatelh
FS_L_Rostralmiddlefrontal_GrayVol = smri_vol_cdk_rrmdfrlh
FS_L_Superiorfrontal_GrayVol = smri_vol_cdk_sufrlh
FS_L_Superiorparietal_GrayVol = smri_vol_cdk_supllh
FS_L_Superiortemporal_GrayVol = smri_vol_cdk_sutmlh
FS_L_Supramarginal_GrayVol = smri_vol_cdk_smlh
FS_L_Frontalpole_GrayVol = smri_vol_cdk_frpolelh
FS_L_Temporalpole_GrayVol = smri_vol_cdk_tmpolelh
FS_L_Transversetemporal_GrayVol = smri_vol_cdk_trvtmlh
FS_L_Insula_GrayVol = smri_vol_cdk_insulalh
FS_R_Bankssts_GrayVol = smri_vol_cdk_banksstsrh
FS_R_Caudalanteriorcingulate_GrayVol = smri_vol_cdk_cdacaterh
FS_R_Caudalmiddlefrontal_GrayVol = 	smri_vol_cdk_cdmdfrrh
FS_R_Cuneus_GrayVol = smri_vol_cdk_cuneusrh
FS_R_Entorhinal_GrayVol = smri_vol_cdk_ehinalrh
FS_R_Fusiform_GrayVol = smri_vol_cdk_fusiformrh
FS_R_Inferiorparietal_GrayVol = smri_vol_cdk_ifplrh
FS_R_Inferiortemporal_GrayVol = smri_vol_cdk_iftmrh
FS_R_Isthmuscingulate_GrayVol = smri_vol_cdk_ihcaterh
FS_R_Lateraloccipital_GrayVol = smri_vol_cdk_loccrh
FS_R_Lateralorbitofrontal_GrayVol = smri_vol_cdk_lobfrrh
FS_R_Lingual_GrayVol = smri_vol_cdk_lingualrh
FS_R_Medialorbitofrontal_GrayVol = smri_vol_cdk_mobfrrh
FS_R_Middletemporal_GrayVol = smri_vol_cdk_mdtmrh
FS_R_Parahippocampal_GrayVol = smri_vol_cdk_parahpalrh
FS_R_Paracentral_GrayVol = smri_vol_cdk_paracnrh
FS_R_Parsopercularis_GrayVol = smri_vol_cdk_parsopcrh
FS_R_Parsorbitalis_GrayVol = smri_vol_cdk_parsobisrh
FS_R_Parstriangularis_GrayVol = smri_vol_cdk_parstgrisrh
FS_R_Pericalcarine_GrayVol = smri_vol_cdk_periccrh
FS_R_Postcentral_GrayVol = smri_vol_cdk_postcnrh
FS_R_Posteriorcingulate_GrayVol = 	smri_vol_cdk_ptcaterh
FS_R_Precentral_GrayVol = smri_vol_cdk_precnrh
FS_R_Precuneus_GrayVol = smri_vol_cdk_pcrh
FS_R_Rostralanteriorcingulate_GrayVol = smri_vol_cdk_rracaterh
FS_R_Rostralmiddlefrontal_GrayVol = smri_vol_cdk_rrmdfrrh
FS_R_Superiorfrontal_GrayVol = smri_vol_cdk_sufrrh
FS_R_Superiorparietal_GrayVol = smri_vol_cdk_suplrh
FS_R_Superiortemporal_GrayVol = smri_vol_cdk_sutmrh
FS_R_Supramarginal_GrayVol = smri_vol_cdk_smrh
FS_R_Frontalpole_GrayVol = smri_vol_cdk_frpolerh
FS_R_Temporalpole_GrayVol = smri_vol_cdk_tmpolerh
FS_R_Transversetemporal_GrayVol = smri_vol_cdk_trvtmrh
FS_R_Insula_GrayVol = smri_vol_cdk_insularh
